Time Series Modeling of Varying Complexity Captures Subdiffusive Solute Dynamics and Predicts Long Timescale Behavior in Nanoscale Pores.

### 2019-11-21 Ben_Manuscripts/stochastic_transport/Draft.tex
Getting peak of passage time distributions

  \subsection{Solute Flux}

>>>>

  \subsection{Mean First Passage Time}

  We used the mean first passage time (MFPT) in order to quantify how long it would take a 
  typical particle, parameterized with the above models, to travel across a membrane pore
  of length $L$. To measure this quantity, we simulated realizations of 10000 particle 
  trajectories, started at the pore entrance ($z=0$). In the case of uncorrelated hops, one
  can continuously draw from the hop length distribution until $z \geq L$ (Or $-L$ for 
  the sake of computational efficiency). The length of time between the last time the 
  particle crossed $z=0$ and the end of the trajectory gives a single passage time. 
  When particle hops are correlated, as they are in all cases of this work, we cannot 
  continuously construct the particle trajectories. Rather, we must generate trajectories
  of length $n$ and measure the length of the sub-trajectory which traverses from $0$ 
  to $L$ without becoming negative. It is important to choose a value of $n$ sufficiently
  large that all trajectories reach $L$, or else the mean first passage time will 
  be underestimated.

  Our definition of the mean first passage time differs from more standard treatments.
  The setup of our system is consistent with a one dimensional interval with two absorbing 
  boundaries. In the absence of an external force and a constant diffusion coefficient, $D$, 
  the mean first passage time is simply:
  \begin{equation}
  T = \frac{z_0(L - z_0)}{2D}
  \end{equation}
  where $z_0$ is the initial position of particle trajectories.~\cite{gitterman_mean_2000}
  Of course that implies a conventional MFPT of 0 since particles overwhelmingly exit the
  pore at $z=0$. Therefore, we chose only to include trajectories in the MFPT calculation 
  which cross the boundary at $L$. We are unaware of an analytical form of the MFPT or 
  the distribution of passage times describing our system even in the simplest case of 
  Brownian increments.

  In the absence of an analytical equation for the MFPT, we instead report the location of
  the peak of the passage time distribution. This has the added advantage of treating
  cases where the passage time distribution diverges and no mean exists. While we will
  call the peak in the distribution the MFPT, it is important to recognize that this 
  value is more representative of a typical passage time rather than a mean.

  % BJC: concentration profile stuff
%  One would then segment the trajectory
%  each time it crosses $0$ and reflect all of the negative trajectories. The ensemble of
%  trajectories is consistent with the fraction of partic
